%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 2.0 (6/7/2019)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[14pt]{article} % Default document font size

\input{structure.tex} % Include the file specifying the document structure and styling

% Set PDF meta-information
\hypersetup{
	pdftitle={Benedikt Singer - CV},
	pdfauthor={Benedikt Singer}
}

%----------------------------------------------------------------------------------------

\begin{document}
%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION
%----------------------------------------------------------------------------------------
\section*{\Huge{Benedikt Singer}}

\faicon{envelope} $\:$ Email 1: \href{mailto:bsinger@uw.edu}{bsinger@uw.edu}\\
\faicon{envelope} $\:$ Email 2: \href{mailto:singerbenedikt1@gmail.com}{singerbenedikt1@gmail.com}\\
\faicon{github} $\:$ GitHub: \href{https://github.com/benediktsinger}{benediktsinger}\\
\faicon{linkedin} $\:$ Linkedin: \href{https://www.linkedin.com/in/benedikt-singer-521689281}{Benedikt Singer}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section*{Experiences}

\subsection*{Academic Internships}

\years{2023/01-\\ 2023/09}\textsc{Master's Thesis} University of Washington - Institute of Protein Design; \\Fine-tuning a SE3-equivariant transformer (RoseTTAfold2) on antibody interactions; \\
\textit{Supervisor:} Prof. David Baker\\
\\
\years{2022/02-\\ 2022/11}\textsc{Master's Thesis} Institute of Science and Technology Austria; \\Software Development using C++ and Python in a Cryo-ET/EM data pipeline; \\
\textit{Supervisor:} Ass. Prof. Florian Schur\\
\\
\years{2021/07-\\2021/09}\textsc{Internship} Vienna University of Technology ICEBE;\\ Extracting mtDNA of \textit{Aspergillus} species using a metagenomic assembler (metaSPAdes) based software; \\
\textit{Supervisor:} Ass. Prof. Matthias Steiger\\
\\
\years{2020/01-\\2020/02}\textsc{Bachelor's Thesis} Vienna University of Technology ICEBE; \\Screening of cyanobacteria using FACS and HPLC; \\
\textit{Supervisor:} Assoc. Prof. Oliver Spadiut

\subsection*{Teaching}

\years{2022/02-\\2022/07}\textsc{Tutor} Software Development in C++; University of Applied Science Campus Vienna\\

\years{2023/04-\\2023/09}\textsc{Mentor} Rotation grad student project; University of Washington - Institute of Protein Design


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\section*{Journal articles}

\years{2021} Doppler P., Kriechbaum R., Singer B., Spadiut O. Make microalgal cultures axenic again – a fast and simple workflow utilizing fluorescence-activated cell sorting. \emph{Journal of Microbiological Methods}, 2021. \url{https://doi.org/10.1016/j.mimet.2021.106256} \\

\years{In prep.} Identifying actin binding proteins using a novel classification pipeline on ultrastrucutral actin filament networks and combining SPA cryo-EM with cryo-ET\\

\years{In prep.} Fine-tuning and improving Rosettafold2 on antibody-target interactions without providing structural information\\

\newpage

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section*{Education}

\years{2020-\\10/2023}\textsc{Master of Science/Diplom-Ingenieur}: Technical Chemistry in biotechnology and bioanalytics,\\ Vienna University of Technology; EQF Level: 7\\
\\
\years{2020-\\2022}\textsc{Extension curriculum}: Digital competences (30 ECTS),\\ Vienna University of Technology\\
\\
\years{2020-\\2022}\textsc{Master of Science}: Bioinformatics (with distinction),\\ University of Applied Science Campus Vienna; EQF Level: 7\\
\\
\years{2017-\\2020}\textsc{Bachelor of Science}: Technical Chemistry,\\ Vienna University of Technology; EQF Level: 6\\


%--------------------------------------------------------------------------------------------

\section*{Skills}

\subsection*{Language Skills}

\textsc{French} \textit{Oral and Written}: B1 \\
\textsc{English} \textit{Oral and Written}: C1/B2

\subsection*{Digital Skills}

\textsc{Programming and Scripting:} C++ , Python (scientific Python and PyTorch), R

\textsc{Database:} SQL (SQLite)

\textsc{Text Processing:} Open Office, Markdown, \LaTeX

\textsc{Other:} Version Control (Git), Linux (Shellscripting), Modelling (UML)

%--------------------------------------------------------------------------------------------

\section*{References}

\textsc{Prof. David Baker}\\University of Washington, Director of the Institute of Protein Design\\
\href{mailto:dabaker@uw.edu}{dabaker@uw.edu}\\
\\
\textsc{FH-Prof. Alexandra Graf}\\University of Applied Science Campus Vienna\\
\href{mailto:alexandra.graf@fh-campuswien.ac.at}{alexandra.graf@fh-campuswien.ac.at}\\
\\
\textsc{Ass. Prof. Florian Schur}\\Institute of Science and Technology Austria\\
\href{mailto:Florian.Schur@ist.ac.at}{Florian.Schur@ist.ac.at}\\
\\
\textsc{Prof. Martina Marchetti-Deschmann}\\Vienna University of Technology\\
\href{mailto:martina.marchetti-deschmann@tuwien.ac.at}{martina.marchetti-deschmann@tuwien.ac.at}\\

%\subsection*{Hobbies and Interests}

%(Trail)-Running, Ultramarathon, Yoga, Documentaries, Classical Music

%\subsection*{Various employments}
%
%\years{2013/07}\textsc{Industrial Facility Cleaner} Fa. ISS, Linz\\
%\\
%\years{2014/07, \\ 2015/07}\textsc{Industrial Facility Cleaner} Fa. Service-Team, Linz\\
%\\
%\years{2017/08, \\ 2016/08}\textsc{Electrician} Fa. Klampfer, Linz\\
%\\
%\years{2015/09-\\2021}\textsc{Promoter} MyTeam-Agentur GmbH, Vienna\\
%\\
%\years{2019/12}\textsc{Event Organiser} MyTeam-Agentur GmbH, Vienna\\
%\\
%\years{2020/08}\textsc{Literature Researcher} PK-Techventures; Technologies for paper and pulp industry\\
%\\
%\years{2021/04}\textsc{Literature Researcher Assistant Team Lead} PK-Techventures; Coastal protection technologies


\end{document}
